---
title: "Country Scenario Overview: `r cfg$rname`"
date: \today
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: true
---
  
  This is the national scenario overview for `r cfg$rname`, it contains graphs for the most important national indicators.
  
\section{National results}

\subsection{GDP and Population over time in Baseline scenarios}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

plot_line(reg=cfg$r,dt=all,vars=c("GDP|MER","Population"),cats=c("Baseline"),title="Socio-Economic Indicators",file_pre="gdp_pop_line")   

invisible(dev.off())

```
\subsection{Key energy system characteristics}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

vars <- c('Final Energy','Primary Energy','Emissions|CO2')#'Population')
cats <- c("Baseline","Optimal 450")

plot_funnel(reg=cfg$r,dt=all,vars=vars,cats=cats,title="Key energy system characteristics",file_pre="fe_pe_co2_funnel")   


invisible(dev.off())

```
\subsection{Kaya Factors over time}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

vars <- c("GDP per capita|MER","Energy Intensity of GDP|MER","Carbon Intensity of FE","Emissions per capita")
cats <- c("Baseline","Optimal 450")

plot_funnel(reg=cfg$r,dt=all,vars=vars,cats=cats,title="Kaya factors",file_pre="kaya_funnel")   

invisible(dev.off())

```
\subsection{Elasticity of models: relative abatement as function of Carbon price}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c(x="Price|Carbon",y="relative Abatement|CO2")
cats <- c("Baseline","Optimal 450")
plot_scatter(reg=cfg$r,dt=all,vars_to_spread=vars,cats=cats,title="Relative Abatement",file_pre="relAb_co2pr_scatter",xlog=T)   

invisible(dev.off())

```

\subsection{Elasticity of models: Carbon Intensity vs. Energy Intensity}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c(x="Energy intensity reduction rel. to Base",y="Carbon intensity reduction rel. to Base")
cats <- c("Baseline","Optimal 450")
plot_scatter(reg=cfg$r,dt=all,vars_to_spread=vars,cats=cats,title="Carbon Intensity vs. Energy Intensity",file_pre="ci_ei_scatter")   

invisible(dev.off())

```

\subsection{Emissions over GDP}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c(x="GDP|MER",y="Final Energy")
cats <- c("Baseline","Optimal 450")
plot_scatter(reg=cfg$r,dt=all,vars_to_spread=vars,cats=cats,title="Socio-Economic Indicators",file_pre="gdp_fe_scatter")   

invisible(dev.off())

```
