---
title: "Country Scenario Overview: `r cfg$rname`"
date: \today
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: true
---
  
  This is the national scenario overview for `r cfg$rname`, it contains graphs for the most important national indicators.
  
\section{National results}

\subsection{GDP and Population over time in Baseline scenarios}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

plot_line(reg=cfg$r,dt=all,vars=c("GDP|MER","Population"),cats=c("Baseline"),title="Socio-Economic Indicators",file_pre="gdp_pop_line")   

invisible(dev.off())

```
\subsection{Key energy system characteristics}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

vars <- c('Final Energy','Primary Energy','Emissions|CO2|FFI')#'Population')
cats <- c("Baseline","Global 450 / S3","Global 500")

plot_funnel(reg=cfg$r,dt=all[Year<=2050],vars=vars,cats=cats,title="Key energy system characteristics",file_pre="fe_pe_co2_funnel",glob_lines=T,xlim=c(2000,2050))   


invisible(dev.off())

```
\subsection{Kaya Factors over time}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

vars <- c("GDP per capita|MER","Energy Intensity of GDP|MER","Carbon Intensity of FE","Emissions per capita")
cats <- c("Baseline","Global 450 / S3")

plot_funnel(reg=cfg$r,dt=all[Year<=2050],vars=vars,cats=cats,title="Kaya factors",file_pre="kaya_funnel",glob_lines=T,xlim=c(2000,2050))   

invisible(dev.off())

```
\subsection{Elasticity of models: relative abatement as function of Carbon price}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c(x="Price|Carbon",y="relative Abatement|CO2")
cats <- c("Global 450 / S3")
plot_scatter(reg=cfg$r,dt=all[Year<=2050],vars_to_spread=vars,cats=cats,title="Relative Abatement",file_pre="relAb_co2pr_scatter",xlog=T,xlim=c(10,1000))   

invisible(dev.off())

```

\subsection{Elasticity of models: Carbon Intensity vs. Energy Intensity}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c(x="Energy intensity reduction rel. to Base",y="Carbon intensity reduction rel. to Base")
cats <- c("Global 450 / S3")
plot_scatter(reg=cfg$r,dt=all[Year<=2050],vars_to_spread=vars,cats=cats,title="Carbon Intensity vs. Energy Intensity",file_pre="ci_ei_scatter")   

invisible(dev.off())

```

\subsection{Final Energy over GDP}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c(x="GDP|MER",y="Final Energy")
cats <- c("Baseline","Global 450 / S3")
plot_scatter(reg=cfg$r,dt=all[Year<=2050],vars_to_spread=vars,cats=cats,title="Socio-Economic Indicators",file_pre="gdp_fe_scatter")   

invisible(dev.off())

```

\subsection{Energy Mix - Primary Energy}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Primary Energy","Primary Energy|Coal|w/o CCS","Primary Energy|Coal|w/ CCS","Primary Energy|Gas|w/o CCS","Primary Energy|Gas|w/ CCS","Primary Energy|Oil|w/o CCS","Primary Energy|Oil|w/ CCS","Primary Energy|Biomass|w/o CCS","Primary Energy|Biomass|w/ CCS","Primary Energy|Nuclear","Primary Energy|Hydro","Primary Energy|Wind","Primary Energy|Solar","Primary Energy|Geothermal","Primary Energy|Other")
cats <- c("Baseline","Global 450 / S3")
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Primary Energy (EJ/yr)",file_pre="pe_area",xlim=c(2000,2050))   

invisible(dev.off())

```

\subsection{Energy Mix - Electricity}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Secondary Energy|Electricity","Secondary Energy|Electricity|Coal|w/o CCS","Secondary Energy|Electricity|Coal|w/ CCS","Secondary Energy|Electricity|Gas|w/o CCS","Secondary Energy|Electricity|Gas|w/ CCS","Secondary Energy|Electricity|Oil|w/o CCS","Secondary Energy|Electricity|Oil|w/ CCS","Secondary Energy|Electricity|Biomass|w/o CCS","Secondary Energy|Electricity|Biomass|w/ CCS","Secondary Energy|Electricity|Nuclear","Secondary Energy|Electricity|Hydro","Secondary Energy|Electricity|Wind","Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Geothermal","Secondary Energy|Electricity|Other")
cats <- c("Baseline","Global 450 / S3")
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Electricity Generation (EJ/yr)",file_pre="ele_area",xlim=c(2000,2050))   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy by carrier}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy","Final Energy|Electricity","Final Energy|Gases","Final Energy|Heat","Final Energy|Hydrogen","Final Energy|Liquids","Final Energy|Other","Final Energy|Solids")
cats <- c("Baseline","Global 450 / S3")
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_c_area",xlim=c(2000,2050))   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy by sector}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy","Final Energy|Transportation","Final Energy|Residential and Commercial","Final Energy|Industry","Final Energy|Other Sector")
cats <- c("Baseline","Global 450 / S3")
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_s_area")   

invisible(dev.off())

```



```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
# \subsection{Energy Mix - Primary Energy shares}
# For ternary plots, 
#vars_to_spread <- c(x="Primary Energy|Coal",y="Primary Energy|Oil",z="Primary Energy|Non-Biomass Renewables")
#cats <- c("Baseline","Global 450 / S3")
#plot_ternary(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="pe_tern",yearmax=2050)   

#invisible(dev.off())

```