---
title: "Country Scenario Overview: `r cfg$rname`"
date: \today
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: true
---
  
  This is the national scenario overview for `r cfg$rname`, it contains graphs for the most important national indicators.
  
\section{National results}

\subsection{GDP and Population over time in Baseline scenarios}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
#general setting for the whole sheet:
#all scenarios with national model scenarios available
if(cfg$r=="JPN"){
  nat_cats <- intersect(unique(all[Scope=="national"]$Category),c("NoPOL","NPi","INDC","2020_low","2030_high"))
} else  {
  nat_cats <- intersect(unique(all[Scope=="national"]$Category),c("NoPOL","NPi","INDC","2030_low","2030_high"))
}

plot_line(reg=cfg$r,dt=all,vars=c("GDP|MER","Population"),cats=c("NoPOL"),title="Socio-Economic Indicators",file_pre="gdp_pop_line")   

invisible(dev.off())

```
\subsection{Macro economic results}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

plot_line(reg=cfg$r,dt=all,vars=c("Policy Cost|Consumption Loss","Policy Cost|GDP Loss"),cats=c("2030_high"),title="Policy Costs in 2030_high scenarios",file_pre="cons_gdp_loss_line")   

invisible(dev.off())

```

\subsection{Key energy system characteristics}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

vars <- c('Final Energy','Primary Energy','Emissions|CO2|FFI')#'Population')
cats <- nat_cats

plot_funnel(reg=cfg$r,dt=all[period<=2050],vars=vars,cats=cats,title="Key energy system characteristics",file_pre="fe_pe_co2_funnel",glob_lines=T,xlim=c(2000,2050))   


invisible(dev.off())

```

\subsection{Kyoto gas emissions over time}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

plot_funnel(reg=cfg$r,dt=all,vars=c("Emissions|Kyoto Gases"),cats=nat_cats,title="Kyoto gas emissions",file_pre="GHG_funnel",glob_lines=T,xlim=c(2000,2050))   

invisible(dev.off())

```

\subsection{Kaya Factors over time}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
if (!identical(character(0),intersect(nat_cats,c("NoPOL","2020_low","2030_low")) )){
vars <- c("GDP per capita|MER","Energy Intensity of GDP|MER","Carbon Intensity of FE","Emissions per capita")
cats <- intersect(nat_cats,c("NoPOL","2020_low","2030_low"))

plot_funnel(reg=cfg$r,dt=all[period<=2050],vars=vars,cats=cats,title="Kaya factors",file_pre="kaya_funnel",glob_lines=T,xlim=c(2000,2050))   
}
invisible(dev.off())

```

\subsection{Carbon budget 2011-2050}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c("Carbon budget")
cats <- unique(all$Category)

plot_bar(reg=cfg$r,dt=all[period==2050],vars="Carbon budget",cats=cats,lab="Carbon budget (Gt CO2; 2011-2050)",file_pre="carbon_budget_bar50",ref_line=T)

invisible(dev.off())

```
\subsection{Carbon budget 2011-2100}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c("Carbon budget")
cats <- unique(all$Category)

plot_bar(reg=cfg$r,dt=all[period==2100],vars="Carbon budget",cats=cats,lab="Carbon budget (Gt CO2; 2011-2100)",file_pre="carbon_budget_bar",ref_line=T)

invisible(dev.off())

```
\subsection{Carbon budget 2051-2100}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c("Carbon budget")
cats <- unique(all$Category)

plot_bar(reg=cfg$r,dt=all[period==2105],vars="Carbon budget",cats=cats,lab="Carbon budget (Gt CO2; 2051-2100)",file_pre="carbon_budget_bar",ref_line=F)

tab <- all[variable=="Carbon budget"]
tab <- data.frame(period=tab$period, Category =tab$Category, value =tab$value, model = tab$model)
tab <- dcast(tab,Category + value ~ period)

invisible(dev.off())

```

\subsection{Peak year CO2}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c("Peak year|CO2")
cats <- unique(all$Category)

plot_point(reg=cfg$r,dt=all,vars="Peak year|CO2",cats=cats,lab="Peak year CO2 emissions",file_pre="peak_CO2_point",ref_line=F)

invisible(dev.off())

```

\subsection{Peak year Kyoto Gases}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c("Peak year|Kyoto Gases")
cats <- unique(all$Category)

plot_point(reg=cfg$r,dt=all,vars="Peak year|Kyoto Gases",cats=cats,lab="Peak year Kyoto Gas emissions",file_pre="peak_Kyoto_point",ref_line=F)

invisible(dev.off())

```

\subsection{Elasticity of models: relative abatement as function of Carbon price}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
if (!identical(character(0),intersect(nat_cats,c("2020_low","2030_low")) )){
  # Please specify exactly two variables and assign them to x and y
  vars <- c(x="Price|Carbon",y="relative Abatement|CO2")
  cats <- intersect(nat_cats,c("2020_low","2030_low"))
  if (dim(all[Scope=="national" & variable=="Price|Carbon"])[1]!=0){
    plot_scatter(reg=cfg$r,dt=all[period<=2050],vars_to_spread=vars,cats=cats,title="Relative Abatement",file_pre="relAb_co2pr_scatter",xlog=T,xlim=c(10,1000))   
  }
}
invisible(dev.off())

```

\subsection{Elasticity of models: Carbon Intensity vs. Energy Intensity}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
if (!identical(character(0),intersect(nat_cats,c("2020_low","2030_low")) )){
# Please specify exactly two variables and assign them to x and y
vars <- c(x="Energy intensity rel. to Base",y="Carbon intensity rel. to Base")
cats <- intersect(nat_cats,c("2020_low","2030_low"))
plot_scatter(reg=cfg$r,dt=all[period<=2050],vars_to_spread=vars,cats=cats,title="Carbon Intensity vs. Energy Intensity",file_pre="ci_ei_scatter")   
}
invisible(dev.off())

```

\subsection{Final Energy over GDP}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
if (!identical(character(0),intersect(nat_cats,c("NoPOL","2020_low","2030_low")) )){
# Please specify exactly two variables and assign them to x and y
vars <- c(x="GDP|MER",y="Final Energy")
cats <- intersect(nat_cats,c("NoPOL","2020_low","2030_low"))
plot_scatter(reg=cfg$r,dt=all[period<=2050],vars_to_spread=vars,cats=cats,title="Socio-Economic Indicators",file_pre="gdp_fe_scatter")   
}
invisible(dev.off())

```

\subsection{Energy Mix - Primary Energy}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Primary Energy","Primary Energy|Coal|w/o CCS","Primary Energy|Coal|w/ CCS","Primary Energy|Gas|w/o CCS","Primary Energy|Gas|w/ CCS","Primary Energy|Oil|w/o CCS","Primary Energy|Oil|w/ CCS","Primary Energy|Biomass|w/o CCS","Primary Energy|Biomass|w/ CCS","Primary Energy|Nuclear","Primary Energy|Hydro","Primary Energy|Wind","Primary Energy|Solar","Primary Energy|Geothermal","Primary Energy|Other","Primary Energy|Secondary Energy Trade")
#plot all scenarios with national model scenarios available
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Primary Energy (EJ/yr)",file_pre="pe_area",xlim=c(2000,2050))   

invisible(dev.off())

```

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
# \subsection{Energy Mix - Primary Energy shares}
# For ternary plots, 
#vars_to_spread <- c(x="Primary Energy|Coal",y="Primary Energy|Oil",z="Primary Energy|Non-Biomass Renewables")
#cats <- c("NoPOL","2020_low")
#plot_ternary(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="pe_tern",yearmax=2050)   

#invisible(dev.off())

```

\subsection{Energy Mix - Electricity}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Secondary Energy|Electricity","Secondary Energy|Electricity|Coal|w/o CCS","Secondary Energy|Electricity|Coal|w/ CCS","Secondary Energy|Electricity|Gas|w/o CCS","Secondary Energy|Electricity|Gas|w/ CCS","Secondary Energy|Electricity|Oil","Secondary Energy|Electricity|Biomass|w/o CCS","Secondary Energy|Electricity|Biomass|w/ CCS","Secondary Energy|Electricity|Nuclear","Secondary Energy|Electricity|Hydro","Secondary Energy|Electricity|Wind","Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Geothermal","Secondary Energy|Electricity|Other")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Electricity Generation (EJ/yr)",file_pre="ele_area",xlim=c(2000,2050))   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy by carrier}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy","Final Energy|Electricity","Final Energy|Gases","Final Energy|Heat","Final Energy|Hydrogen","Final Energy|Liquids","Final Energy|Other","Final Energy|Solids")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_c_area",xlim=c(2000,2050))   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy by sector}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy","Final Energy|Transportation","Final Energy|Residential and Commercial","Final Energy|Industry","Final Energy|Other Sector")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_s_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy in Industry}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy|Industry","Final Energy|Industry|Electricity","Final Energy|Industry|Gases","Final Energy|Industry|Heat","Final Energy|Industry|Hydrogen","Final Energy|Industry|Liquids","Final Energy|Industry|Other","Final Energy|Industry|Solids")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_industry_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy in Residential and Commercial}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy|Residential and Commercial","Final Energy|Residential and Commercial|Electricity","Final Energy|Residential and Commercial|Gases","Final Energy|Residential and Commercial|Heat","Final Energy|Residential and Commercial|Hydrogen","Final Energy|Residential and Commercial|Liquids","Final Energy|Residential and Commercial|Other", "Final Energy|Residential and Commercial|Solids")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_buildings_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy in Transportation}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy|Transportation","Final Energy|Transportation|Electricity","Final Energy|Transportation|Gases","Final Energy|Transportation|Hydrogen","Final Energy|Transportation|Liquids","Final Energy|Transportation|Other")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Final Energy (EJ/yr)",file_pre="fe_transport_area")   

invisible(dev.off())

```

\subsection{Carbon sequestration - CCS}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Carbon Sequestration|CCS","Carbon Sequestration|CCS|Biomass","Carbon Sequestration|CCS|Fossil")
cats <- nat_cats
plot_area(reg=cfg$r,dt=all,vars=vars,cats=cats,lab="Carbon sequestration (Mt CO2/yr)",file_pre="cs_CCS_area")   

invisible(dev.off())
```
