---
title: "Country Scenario Overview: `reg`"
date: \today
output:
  pdf_document:
    toc: true
    toc_depth: 5
    number_sections: true
---
  
  This is an overview of the national scenarios for `reg`
  
\section{National results}

\subsection{PE and FE trajectories}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
#general setting for the whole sheet:
#all scenarios with national model scenarios available

  nat_scens <- intersect(c("NoPOL","NPi","INDC","NPi2020_high","NPi2020_low","INDC2030_high","INDC2030_low"),unique(all[Scope=="national"]$scenario))

vars <- c('Final Energy','Primary Energy')#'Population')
scens <- nat_scens
dt = all[region == reg & period<=2050 & Scope=="national" & scenario %in% scens]
dt$scenario <- factor(dt$scenario, levels = scens, ordered = T)
  

plot_line_nat(reg=reg,dt=dt,vars=vars,scens=scens,title="Primary and final energy",file_pre="nat_pe_fe_lines")   


invisible(dev.off())

```

\subsection{Emissions}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c('Emissions|CO2','Emissions|CO2|Energy','Emissions|CO2|Energy and Industrial Processes')#'Population')

plot_line_nat(reg=reg,dt=dt,vars=vars,scens=scens,title="Emissions",file_pre="nat_co2_lines")   


invisible(dev.off())

```

\subsection{Carbon Prices}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
vars <- c('Price|Carbon','Mitigation Cost|Consumption Loss')#'Population')
if(dim(dt[variable %in% vars])[1]>0){
plot_line_nat(reg=reg,dt=dt,vars=vars,scens=scens,title="Key energy system characteristics",file_pre="nat_co2price_lines")   
}

invisible(dev.off())

```
\subsection{Energy emission decomposition}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Emissions|CO2|Energy","Emissions|CO2|Energy|Demand|Transportation","Emissions|CO2|Energy|Demand|Residential and Commercial","Emissions|CO2|Energy|Demand|Industry","Emissions|CO2|Energy|Supply")
#plot all scenarios with national model scenarios available
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Primary Energy (EJ/yr)",file_pre="nat_emi_area")   

invisible(dev.off())

```


\subsection{Carbon sequestration - CCS}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Carbon Sequestration|CCS","Carbon Sequestration|CCS|Biomass","Carbon Sequestration|CCS|Fossil")
if(dim(dt[variable %in% vars])[1]>0){
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Carbon sequestration (Mt CO2/yr)",file_pre="nat_CCS_area")   
}
invisible(dev.off())
```

\subsection{Energy Mix - Primary Energy}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Primary Energy","Primary Energy|Hydro","Primary Energy|Coal|w/o CCS","Primary Energy|Coal|w/ CCS","Primary Energy|Gas|w/o CCS","Primary Energy|Gas|w/ CCS","Primary Energy|Oil|w/o CCS","Primary Energy|Oil|w/ CCS","Primary Energy|Biomass|w/o CCS","Primary Energy|Biomass|w/ CCS","Primary Energy|Nuclear","Primary Energy|Wind","Primary Energy|Solar","Primary Energy|Geothermal","Primary Energy|Other","Primary Energy|Secondary Energy Trade")
#plot all scenarios with national model scenarios available
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Primary Energy (EJ/yr)",file_pre="nat_pe_area")   

invisible(dev.off())

```


\subsection{Energy Mix - Electricity}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# Please specify exactly two variables and assign them to x and y
vars <- c("Secondary Energy|Electricity","Secondary Energy|Electricity|Hydro","Secondary Energy|Electricity|Coal|w/o CCS","Secondary Energy|Electricity|Coal|w/ CCS","Secondary Energy|Electricity|Gas|w/o CCS","Secondary Energy|Electricity|Gas|w/ CCS","Secondary Energy|Electricity|Oil","Secondary Energy|Electricity|Biomass|w/o CCS","Secondary Energy|Electricity|Biomass|w/ CCS","Secondary Energy|Electricity|Nuclear","Secondary Energy|Electricity|Wind","Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Geothermal","Secondary Energy|Electricity|Other")
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Electricity Generation (EJ/yr)",file_pre="nat_ele_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy by carrier}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy","Final Energy|Electricity","Final Energy|Gases","Final Energy|Heat","Final Energy|Hydrogen","Final Energy|Liquids","Final Energy|Other","Final Energy|Solids")
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Final Energy (EJ/yr)",file_pre="nat_fe_c_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy by sector}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy","Final Energy|Transportation","Final Energy|Residential and Commercial","Final Energy|Industry","Final Energy|Other Sector","Final Energy|Non-Energy Use")
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Final Energy (EJ/yr)",file_pre="nat_fe_s_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy in Industry}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy|Industry","Final Energy|Industry|Electricity","Final Energy|Industry|Gases","Final Energy|Industry|Heat","Final Energy|Industry|Hydrogen","Final Energy|Industry|Liquids","Final Energy|Industry|Other","Final Energy|Industry|Solids")
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Final Energy (EJ/yr)",file_pre="nat_fe_industry_area")   

invisible(dev.off())

```

\subsection{Energy Mix - Final Energy in Residential and Commercial}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}

# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy|Residential and Commercial","Final Energy|Residential and Commercial|Electricity","Final Energy|Residential and Commercial|Gases","Final Energy|Residential and Commercial|Heat","Final Energy|Residential and Commercial|Hydrogen","Final Energy|Residential and Commercial|Liquids","Final Energy|Residential and Commercial|Other", "Final Energy|Residential and Commercial|Solids")
if(dim(dt[variable %in% vars])[1]>0){
  plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Final Energy (EJ/yr)",file_pre="nat_fe_buildings_area")   
}
invisible(dev.off())

```

\subsection{Energy Mix - Final Energy in Transportation}

```{r, echo=FALSE,results = 'hide',cache=FALSE, message=FALSE, warning=FALSE,fig.width=8, fig.height=10, dpi=200}
# For area plots, the first entry in vars is interpreted as the total (line_plot on top)
vars <- c("Final Energy|Transportation","Final Energy|Transportation|Electricity","Final Energy|Transportation|Gases","Final Energy|Transportation|Hydrogen","Final Energy|Transportation|Liquids","Final Energy|Transportation|Other")
if(dim(dt[variable %in% vars])[1]>0){
plot_area(reg=reg,dt=dt,vars=vars,cats=unique(dt$Category),lab="Final Energy (EJ/yr)",file_pre="nat_fe_transport_area")   
}
invisible(dev.off())

```

